Effort and Delay Discounting in a Foraging Environment

### 2019-05-08 Cost2/Cost2_prereg_remake.Rmd
up to the OC anova. almost done restructuring the cost 2 script!

# Summarize the proportion complete for GLMs
propComplete <- function(Data = waitData, nSubs = nSubsW, indx = indxWait, type = "Wait") {

    tempProp <- data.frame(SubjID = rep(indx,9),
                           Group = rep(type,nSubs*9),
                           Handling = c(rep(2,nSubs*3), 
                                        rep(10,nSubs*3), 
                                        rep(14,nSubs*3)),
                           Reward = rep(c(rep(4,nSubs),rep(8,nSubs),rep(20,nSubs)),3),
                           propComplete = rep(NA,length(indx)*9),
                           totalTrials = rep(NA,length(indx)*9),
                           totalComplete = rep(NA,length(indx)*9))

      # handling of 2s
      tempProp$propComplete[subj] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==4])
      tempProp$propComplete[subj+nSubs] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==8])
      tempProp$propComplete[subj+(nSubs*2)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==20])
      tempProp$totalTrials[subj] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==4])
      tempProp$totalTrials[subj+nSubs] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==8])
      tempProp$totalTrials[subj+(nSubs*2)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==20])

      # handling of 10s
      tempProp$propComplete[subj+(nSubs*3)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==4])
      tempProp$propComplete[subj+(nSubs*4)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==8])
      tempProp$propComplete[subj+(nSubs*5)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==20])
      tempProp$totalTrials[subj+(nSubs*3)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==4])
      tempProp$totalTrials[subj+(nSubs*4)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==8])
      tempProp$totalTrials[subj+(nSubs*5)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==20])

      # handling of 14s
      tempProp$propComplete[subj+(nSubs*6)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==4])
      tempProp$propComplete[subj+(nSubs*7)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==8])
      tempProp$propComplete[subj+(nSubs*8)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==20])
      tempProp$totalTrials[subj+(nSubs*6)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==4])
      tempProp$totalTrials[subj+(nSubs*7)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==8])
      tempProp$totalTrials[subj+(nSubs*8)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==20])

    return(tempProp)

@@

# minimize the negative log likelihood
optimizeOCModel <- function(Data, Algorithm = "NLOPT_LN_NEWUOA") {
  # Prep data
  handling <- Data$Handling
  reward <- Data$Reward
  choice <- Data$Choice

@@

@@

dataAll <- tibble(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         SubjID = as.integer(substring(SubjID, 0, 3))) %>%
  unnest() %>%
  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"),
         optimal = case_when(
          (Handling == 10 & Reward < 8) ~ 0,
          (Handling == 14 & Reward < 20) ~ 0,
          TRUE ~ 1
         ))

@@

``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}

# Proportion of forced travels per subject and cost type
propFails <- dataAll %>% 
  filter(Cost != "Wait") %>% 
  group_by(SubjID, Cost) %>% 
  summarise(propFails = mean(Choice == 2)) %>%
  group_by(Cost) %>% 
  summarise(meanQuit = mean(propFails))

# Reaction times ECDFs including offer and in-trial quits
(RTs <- dataAll %>%
  #mutate(RT = ifelse(Choice != 0, RT + 2, RT)) %>%
  filter(Choice < 2) %>% # change this to 1 to reproduce the original plot, since it would only plot the cdf of quits
  ggplot(aes(RT, color = Cost)) + 
    stat_ecdf(lwd = 1.2) +
    geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
    scale_color_manual(values = cols) +
    scale_x_continuous(breaks = seq(14)) +
    theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line = element_line(colour = "black"),
      text = element_text(size = 16)))

@@

``` {r 16.3.2. Pre/Post Break, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
# THIS CODE CAN BE VASTLY IMPROVED, BUT RIGHT NOW IT WORKS SO I WON'T CARE
# This one just plots the correlation between pre-post acceptance rates, both overall and per cell
# The overall acceptance looks great, with mostly consistent rates, and with the physical group accepting slightly less post-break
# However, the per-cell distribution looks messy, although you can still tell that there's a linear relationship
# If I do a linear model predicting post with pre using cell-specific data, the betas are close to 1 and significant (also good R2s). That's good.

# create vdata frames that store acceptance data per combination cell pre-post break
waitB <- data.frame()
waitA <- data.frame()
cogB <- data.frame()
cogA <- data.frame()
physB <- data.frame()
physA <- data.frame()
easyB <- data.frame()
easyA <- data.frame()

# and for overall proportion accepted
waitBAll <- numeric()
waitAAll <- numeric()
cogBAll <- numeric()
cogAAll <- numeric()
physBAll <- numeric()
physAAll <- numeric() 
easyBAll <- numeric()
easyAAll <- numeric()

for (i in seq(nSubsW)){

  # wait
  tempPropB <- aggregate(waitBefore[[i]]$Choice, by = list(waitBefore[[i]]$Handling, waitBefore[[i]]$Reward), FUN = 'mean')
  tempPropA <- aggregate(waitAfter[[i]]$Choice, by = list(waitAfter[[i]]$Handling, waitAfter[[i]]$Reward), FUN = 'mean')
  waitB <- rbind(waitB,tempPropB)
  waitA <- rbind(waitA,tempPropA)
  waitBAll[i] <- mean(waitBefore[[i]]$Choice) 
  waitAAll[i] <- mean(waitAfter[[i]]$Choice)

for (i in seq(nSubsC)){

  # cognitive
  tempPropB <- aggregate(cogBefore[[i]]$Choice, by = list(cogBefore[[i]]$Handling, cogBefore[[i]]$Reward), FUN = 'mean')
  tempPropA <- aggregate(cogAfter[[i]]$Choice, by = list(cogAfter[[i]]$Handling, cogAfter[[i]]$Reward), FUN = 'mean')
  cogB <- rbind(cogB,tempPropB)
  cogA <- rbind(cogA,tempPropA)
  cogBAll[i] <- mean(cogBefore[[i]]$Choice) 
  cogAAll[i] <- mean(cogAfter[[i]]$Choice)

for (i in seq(nSubsP)){

  # physical
  tempPropB <- aggregate(physBefore[[i]]$Choice, by = list(physBefore[[i]]$Handling, physBefore[[i]]$Reward), FUN = 'mean')
  tempPropA <- aggregate(physAfter[[i]]$Choice, by = list(physAfter[[i]]$Handling, physAfter[[i]]$Reward), FUN = 'mean')
  physB <- rbind(physB,tempPropB)
  physA <- rbind(physA,tempPropA)
  physBAll[i] <- mean(physBefore[[i]]$Choice) 
  physAAll[i] <- mean(physAfter[[i]]$Choice)

for (i in seq(nSubsE)){

  # easy
  tempPropB <- aggregate(easyBefore[[i]]$Choice, by = list(easyBefore[[i]]$Handling, easyBefore[[i]]$Reward), FUN = 'mean')
  tempPropA <- aggregate(easyAfter[[i]]$Choice, by = list(easyAfter[[i]]$Handling, easyAfter[[i]]$Reward), FUN = 'mean')
  easyB <- rbind(easyB,tempPropB)
  easyA <- rbind(easyA,tempPropA)
  easyBAll[i] <- mean(easyBefore[[i]]$Choice) 
  easyAAll[i] <- mean(easyAfter[[i]]$Choice)

# Pre-post linear models
prepostLM <- list()
prepostLM$Wait <- lm(waitBAll ~ waitAAll)
prepostLM$Cognitive <- lm(cogBAll ~ cogAAll)
prepostLM$Physical <- lm(physBAll ~ physAAll)
prepostLM$Easy <- lm(easyBAll ~ easyAAll)

prepostSummary <- do.call(rbind, lapply(prepostLM, function(data) c(coef(data)[2], confint(data)[2,])))

@@

``` {r 16.3.2. Plot Pre/Post, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}

# overall proportion
plot(waitBAll,
     waitAAll,
     xlim = c(0,1),
     ylim = c(0,1),
     main = "Proportion accepted pre- and post-midpoint",
     xlab = "Acceptance Rate Before",
     ylab = "Acceptance Rate After",     
     col = cols[1],
     pch = 16)
points(cogBAll,
       cogAAll, 
       col = cols[2],
       pch = 16)
points(physBAll,
       physAAll, 
       col = cols[3],
       pch = 16)
points(easyBAll,
       easyAAll, 
       col = cols[4],
       pch = 16)
lines(seq(0,1,length = 10),
      seq(0,1,length = 10))
legend("bottomright",
       lbls,
       fill = cols,
       cex = 0.8)

# dataAll %>%
#   filter(Choice < 2) %>%
#   group_by(SubjID) %>%
#   #mutate(Block = do.call(c, lapply(c(2,4,6), function(x) {rep(x/2, sum(Block %in% c(x-1, x)))}))) %>%
#   group_by(SubjID, Cost, Block) %>%
#   summarise(propAccept_subj = mean(Choice)) %>%
#   group_by(Cost, Block) %>%
#   summarize(propAccept = mean(propAccept_subj),
#             seAccept = sd(propAccept_subj)/sqrt(nSubjs)) %>%
#   ggplot(aes(Block, propAccept, fill = Cost)) +
#     geom_point(size = 2, pch = 21, color = "black") +
#     geom_errorbar(aes(ymin=propAccept - seAccept, ymax=propAccept + seAccept, color = Cost), width = 0.1) +
#     geom_line(aes(color = Cost)) +
#     ylim(0.5, 1) +
#     scale_x_continuous(breaks = seq(6)) +
#     scale_color_manual(values = cols) +
#     scale_fill_manual(values = cols) +
#     theme_classic()
```

@@

| Condition   |            Beta           |          CI-Low           |          CI-High          |
| :---------- | :-----------------------: | ------------------------: | ------------------------: |
| Wait        | $`r prepostSummary[1,1]`$ | $`r prepostSummary[1,2]`$ | $`r prepostSummary[1,3]`$ |
| Cognitive   | $`r prepostSummary[2,1]`$ | $`r prepostSummary[2,2]`$ | $`r prepostSummary[2,3]`$ |
| Physical    | $`r prepostSummary[3,1]`$ | $`r prepostSummary[3,2]`$ | $`r prepostSummary[3,3]`$ |
| Easy        | $`r prepostSummary[4,1]`$ | $`r prepostSummary[4,2]`$ | $`r prepostSummary[4,3]`$ |
Table: Predicting Post-mid acceptance from pre-mid choices: Coefficients and CI.

@@

``` {r 16.3.3. OC modeling, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# Estimate gamma per subject for each group separately
waitOC <- sapply(waitData, function(Data) {optimizeOCModel(Data)$Gamma})
cogOC <- sapply(cogData, function(Data) {optimizeOCModel(Data)$Gamma})
physOC <- sapply(physData, function(Data) {optimizeOCModel(Data)$Gamma})
easyOC <- sapply(easyData, function(Data) {optimizeOCModel(Data)$Gamma})

# Summarize for plotting
summaryOC <- data.frame(Group = rep(cond, each = nSubsC),
                        Gamma = c(waitOC, cogOC, physOC, easyOC))
summaryOC$Group <- factor(summaryOC$Group, levels = cond, ordered = T)

# plot
ggplot(summaryOC, aes(Group, Gamma, fill = Group)) +
  geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
  geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
  geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
  geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
  ylim(0,1.5) +
  labs(title = "Gamma Values per Group", x = "") +
  scale_fill_manual(values = cols) +
  theme_classic()

@@

``` {r 16.3.4. OC cross-validation, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# Compute the OC for pre-midpoint
waitOCbefore <- sapply(waitBefore, function(Data) {optimizeOCModel(Data)$Gamma})
cogOCbefore <- sapply(cogBefore, function(Data) {optimizeOCModel(Data)$Gamma})
physOCbefore <- sapply(physBefore, function(Data) {optimizeOCModel(Data)$Gamma})
easyOCbefore <- sapply(easyBefore, function(Data) {optimizeOCModel(Data)$Gamma})

# Percent correctly predicted by pre-midpoint gamma
# Wait
predictOCWait <- numeric()
for (i in seq(nSubsW)) {
  temp <- (waitAfter[[i]]$Reward > (waitOCbefore[i] * waitAfter[[i]]$Handling))
  temp[temp == TRUE] <- 1
  predictOCWait[i] <- (sum(temp==waitAfter[[i]]$Choice) / length(waitAfter[[i]]$Choice)) * 100 
}

# Cognitive
predictOCCog <- numeric()
for (i in seq(nSubsC)) {
  temp <- (cogAfter[[i]]$Reward > (cogOCbefore[i] * cogAfter[[i]]$Handling))
  temp[temp == TRUE] <- 1
  predictOCCog[i] <- (sum(temp==cogAfter[[i]]$Choice) / length(cogAfter[[i]]$Choice)) * 100 
}

# Physical
predictOCPhys <- numeric()
for (i in seq(nSubsW)) {
  temp <- (physAfter[[i]]$Reward > (physOCbefore[i] * physAfter[[i]]$Handling))
  temp[temp == TRUE] <- 1
  predictOCPhys[i] <- (sum(temp==physAfter[[i]]$Choice) / length(physAfter[[i]]$Choice)) * 100 
}

# Easy
predictOCEasy <- numeric()
for (i in seq(nSubsW)) {
  temp <- (easyAfter[[i]]$Reward > (easyOCbefore[i] * easyAfter[[i]]$Handling))
  temp[temp == TRUE] <- 1
  predictOCEasy[i] <- (sum(temp==easyAfter[[i]]$Choice) / length(easyAfter[[i]]$Choice)) * 100 
}

# Summarize for plotting
summaryOCPredict <- data.frame(Group = rep(cond, each = nSubsC),
                        percentPredicted = c(predictOCWait, predictOCCog, predictOCPhys, predictOCEasy))
summaryOCPredict$Group <- factor(summaryOCPredict$Group, levels = cond, ordered = T)

meanOCPredict <- aggregate(percentPredicted ~ Group, data = summaryOCPredict,FUN = 'mean')

# plot
ggplot(summaryOCPredict, aes(Group, percentPredicted, fill = Group)) +
  #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
  labs(title = "Percent of Choices Correctly Predicted by Gamma per Group", x = "") +
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = cols) +
  labs(y = "Percent Predicted") +
  ylim(0,100) +
  theme_classic()
```

>>>>

@@

# minimize the negative log likelihood
optimizeOCModel <- function(Data, Algorithm = "NLOPT_LN_NEWUOA", simplify = F) {
  # Prep data
  handling <- Data$Handling
  reward <- Data$Reward
  choice <- Data$Choice

@@

  # if doing this with dplyr::do(), return a simplified data.frame instead with the important parameters
  if (simplify) {
    out <- data.frame(out[c(seq(8), 12)])
  }

@@

dataAll <- tibble(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         SubjID = as.integer(substring(SubjID, 0, 3))) %>%
  unnest() %>%
  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         optimal = case_when(
          (Handling == 10 & Reward < 8) ~ 0,
          (Handling == 14 & Reward < 20) ~ 0,
          TRUE ~ 1
         ))

@@

``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# Proportion of forced travels per subject and cost type
propFails <- dataAll %>% 
  filter(Cost != "Wait") %>% 
  group_by(SubjID, Cost) %>% 
  summarise(propFails = mean(Choice == 2)) %>%
  group_by(Cost) %>% 
  summarise(meanQuit = mean(propFails))

# Reaction times ECDFs including offer and in-trial quits
(RTs <- dataAll %>%
  #mutate(RT = ifelse(Choice != 0, RT + 2, RT)) %>%
  filter(Choice < 2) %>% # change this to 1 to reproduce the original plot, since it would only plot the cdf of quits
  ggplot(aes(RT, color = Cost)) + 
    #stat_ecdf(lwd = 1.2, geom = "smooth") +
    geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
    geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
    scale_color_manual(values = cols) +
    scale_x_continuous(breaks = seq(14)) +
    labs(x = "Reaction Time", y = "Proportion Accepted") +
    theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line = element_line(colour = "black"),
      text = element_text(size = 16)))

@@

``` {r 16.3.2. Pre/Post Break, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}

temp <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Cost, Half) %>%
  summarise(pAccepted = mean(Choice)) %>%
  ungroup() %>%
  spread(Half, pAccepted)

# separate by cost type and compute a linear model to predict half 2 from 1
sep <- temp %>% plyr::dlply("Cost", identity)
prepost$LM <- lapply(sep, function(data) {lm(data$Half_2 ~ data$Half_1)})

# get the coefficients and confidence intervals
# and concatenate
prepost$summary <- as.data.frame(cbind(t(sapply(prepost$LM, coefficients)), t(sapply(prepost$LM, confint))))
colnames(summary_prepost) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
```

@@

``` {r 16.3.2. Plot Pre/Post, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
prepost$plot <- dataAll %>%
                filter(Choice < 2) %>%
                group_by(SubjID, Cost) %>%
                summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
                          propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
                ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
                geom_point(size = 3, pch = 21, color = "black") +
                scale_fill_manual(values = cols) +
                xlim(0,1) +
                ylim(0,1) +
                geom_abline(slope = 1, intercept = 0, lty = 2) +
                theme(panel.grid.major = element_blank(),
                    panel.grid.minor = element_blank(),
                    panel.background = element_blank(),
                    axis.line = element_line(colour = "black"),
                    text = element_text(size = 16)))
```

@@

``` {r 16.3.2. prepost table, pander}
panderOptions("digits", 2)
pander(prepost$summary, style = "rmarkdown", split.table = 110)
```

@@

``` {r 16.3.3. OC modeling, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# group
summaryOC <- list()
summaryOC$all <- dataAll %>%
                 filter(Choice < 2) %>%
                 group_by(Cost, SubjID) %>%
                 do(optimizeOCModel(., simplify = T))

# plot
(summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
                      geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
                      geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
                      geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
                      geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
                      ylim(0,1.5) +
                      labs(title = "Gamma Values per Group", x = "") +
                      scale_fill_manual(values = cols) +
                      theme(panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        panel.background = element_blank(),
                        axis.line = element_line(colour = "black"),
                        text = element_text(size = 16)))

@@

``` {r 16.3.4. OC cross-validation, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# Compute the OC for pre-midpoint
summaryOC$pre <- dataAll %>%
                 filter(Choice < 2, Half == "Half_1") %>%
                 group_by(Cost, SubjID) %>%
                 do(optimizeOCModel(., simplify = T)) %>%
                 ungroup() %>%
                 select(SubjID, Gamma)

# let's add the gammas to the second half data and estimate prop predicted on the second half
summaryOC$predicted <- dataAll %>%
                 filter(Choice < 2, Half == "Half_2") %>%
                 group_by(Cost, SubjID) %>%
                 left_join(summaryOC$pre) %>%
                 mutate(OC = Handling * Gamma,
                        predicted = Reward > OC) %>% 
                 summarise(percentPredicted = mean(predicted == Choice) * 100)

# plot
(summaryOC$predictPlot <- ggplot(summaryOC$predicted, aes(Cost, percentPredicted, fill = Cost)) +
                          labs(x = "") +
                          geom_boxplot(show.legend = F) +
                          scale_fill_manual(values = cols) +
                          labs(y = "Percent Predicted") +
                          ylim(0,100) +
                          theme(panel.grid.major = element_blank(),
                          panel.grid.minor = element_blank(),
                          panel.background = element_blank(),
                          axis.line = element_line(colour = "black"),
                          text = element_text(size = 16)))
